\textls[-0]{\thetitle}

### 2022-11-11 agda-files.tex
itemize agda files

@@

This is the first QIIT-model we give. A QIIT-model can be roughly consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here, the syntactic translation model is mapping to (a subpart of) the original QIIT data (itself).

>>>>

In the ``Other supplemental material'' section of the submission, we
include the complete formalization of \TT.
It consists of four files in Agda syntax.
%

\begin{description}[
    itemsep=.5ex,topsep=.6ex,
    labelsep=1.5ex,
    leftmargin=6.5ex,
%   labelindent=3.5ex,
    font=\ttfamily\bfseries,
]

\item[Syntax.agda]

This file contains the syntactic typing rules of \TT.
We use the style of intrinsically typed syntax \cite{chapman2009type},
which allows only well typed \TT types and terms to be constructed.
The use of intrinsically typed syntax puts our formalization on a more
rigorous footing.

\item[Semantic.agda]

This file defines the standard model from which
\cref{thm:consistency} (consistency) follows.

\item[Canonicity.agda]

This file defines the logical-relations model from which
\cref{thm:canonicity} (canonicity) follows.

\item[SynTranslation.agda]

We also provide a third model that serves as a translation that ``compiles
away'' the novel features---most notably, linkages---introduced by \TT.
As is similar to the first two models, 
a linkage is translated to a non-dependent pair where the
second component is a dependent function (modeling late binding).

\end{description}

All the definitions contained in these files are stated in
terms of a meta\-language supporting quotient inductive-inductive types
(QIITs)~\cite{nordvall2010inductive,altkap2016}.
QIITs support equality constructors, which facilitate the expression of
conversion rules (e.g., \ruleref{tmeq/sub/id}).
%
We note that the current formalization is not checked by Agda because
Agda does not support QIITs natively.
An effort to mechanize the formalization is underway, using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection.

\ifShowOldWriting

\bigskip

@@

This is the first QIIT-model we give. A QIIT-model can be roughly consider as an arbitrary mapping from the QIIT data (our syntax in this case), also respecting the quotient (judgmental equality in this case). Here, the syntactic translation model is mapping to (a subpart of) the original QIIT data (itself).
